Differentiable Optics with {\Large $\partial$}Lux: I - Deep Calibration of Flat Field and Phase with Automatic Differentiation

### 2022-11-10 src/tex/ms.tex
[showyourwork] overleaf sync

\renewcommand{\baselinestretch}{1.0} % Change to 1.65 for double spacing
\usepackage{amsmath,amsfonts,amssymb}
\usepackage{graphicx}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{relsize}
\usepackage{acro}
\acsetup{
  single    = false,
  list/sort  = true,
  cite/group = true,
  cite/group/cmd = \cite,
  cite/group/pre = {},
}

@@

High-precision, high-cadence time series of space photometry from \textit{Kepler} \cite{Borucki2010}, K2 \cite{K2}, TESS \cite{TESS} and CHEOPS \cite{CHEOPS} space telescopes have been revolutionary for exoplanetary science and stellar asr. This increased precision over that last 20 years has also revolutionized asteroseismology [cite multiple papers here], the study of stellar interiors.

>>>>

\renewcommand{\baselinestretch}{1.0} % Change to 1.65 for double spacing
\usepackage{amsmath,amsfonts,amssymb}
\usepackage{graphicx}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
% \usepackage{relsize}
\usepackage{acro}
\acsetup{
  single    = false,
  list/sort  = true,
  cite/group = true,
  cite/group/cmd = \cite,
  cite/group/pre = {},
}

@@

High-precision, high-cadence time series of space photometry from \textit{Kepler} \cite{Borucki2010}, K2 \cite{K2}, TESS \cite{TESS} and CHEOPS \cite{CHEOPS} space telescopes have been revolutionary for exoplanetary science and stellar astrophysics.
